```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(knitr)
library(dplyr)
library(GGally)
library(gridExtra)
library(skimr)
```

## Understanding the data
```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd('C:/Users/Bruno/Documents/Udacity/R/Project')

loanData <- read.csv('../prosperLoanData.csv')
str(loanData)
```

For this first moment, I want to select variables that can be related somehow.
To aid me over this selection process, I am making use of the *ggpairs* function

```{r warning=FALSE, message=FALSE}
# Enabling reproducible results.
set.seed(2)

# Defining a list of columns to be analysed
columns_list <- c('LoanStatus'
                  ,'LoanOriginalAmount'
                  ,'BorrowerRate'
                  ,'EstimatedEffectiveYield'
                  ,'EstimatedLoss'
                  ,'ProsperRating..Alpha.'
                  ,'ProsperScore'
                  ,'CurrentDelinquencies'
                  ,'StatedMonthlyIncome'
                  ,'Recommendations'
                  ,'InvestmentFromFriendsCount')

# Sampling the original dataset so it can be used in a correlation matrix
loanData_samp <- loanData[sample(1:nrow(loanData), 10000), columns_list]

# Plotting the matrix
ggpairs(loanData_samp
        ,axisLabels = 'internal')
```

This plot brings a nice overview over the relationships among the selected variables. By providing scatterplots, histograms, box plots and correlation coeficients, this matrix starts to give some sense over the data behavior. For instance, if we take the variables _BorrowerRate_ and _EstimatedEffectiveYield_, we can see that they are positively correlated by looking to the _coeficient_ and to the _scatterplot_.

DESCRIBE MORE ABOUT THE CORRELATION MATRIX

With that in mind, let's take a closer look to each of this variables.

```{r warning=FALSE, message=FALSE}
#
# ...Removing loan registries that originated before July 2009...
# ...This can be done by subsetting our dataset...
# ...The 'columns_list' defined earlier will be used from now on...
#

ld <- subset(loanData
       ,as.Date(LoanOriginationDate) >= as.Date('2009-07-01')
       ,select = columns_list
       )

str(ld)
```

## Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

Analysing how the Loan Status variable is distributed
```{r warning=FALSE, message=FALSE, echo=FALSE, Univariate_Plots}
LoanStatus_ord_lvl <- c(levels(ld$LoanStatus)[1:6]
      ,levels(ld$LoanStatus)[8:12]
      ,'Past Due (>120 days)')
ld$LoanStatus <- ordered(ld$LoanStatus, levels = LoanStatus_ord_lvl)

ggplot(data = ld
       ,aes(x = LoanStatus)) +
  geom_histogram(color = I('black')
                 ,fill = I('#099DD9')
                 ,stat='count') +
  theme_bw(base_size = 10) +
  theme(axis.text.x=element_text(angle=60,hjust=1))

table(ld$LoanStatus)
```

Analysing how the Loan Amount variable is distributed
```{r warning=FALSE, message=FALSE}
plot1 <- ggplot(data = ld
       ,aes(x = LoanOriginalAmount)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,binwidth = 1000) +
  scale_x_continuous(breaks = seq(0,35000,2500))

plot2 <- ggplot(data = ld
       ,aes(x = LoanOriginalAmount)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,binwidth = .05) +
  scale_x_log10()

grid.arrange(plot1, plot2, nrow=2)

summary(ld$LoanOriginalAmount)
```

Analysing how the Listings are distributed across the Risk Ratings
```{r warning=FALSE, message=FALSE}
# ... Redefining the Rating order, from the Lower to the Higher Risk ...
ProsperRating_ord_lvl <- c('', 'AA', 'A', levels(ld$ProsperRating..Alpha.)[4:8])
ld$ProsperRating..Alpha. <- ordered(ld$ProsperRating..Alpha., levels = ProsperRating_ord_lvl)

ggplot(data = ld
       ,aes(x = ProsperRating..Alpha.)) +
  geom_histogram(color = I('black')
                 ,fill = I('#099DD9')
                 ,stat='count')

# ... Associated effective yield of investment in percent ...
ggplot(data = ld
       ,aes(x = EstimatedEffectiveYield)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=50) +
  scale_x_continuous(breaks = seq(-.2,.32,.04), labels = seq(-.2,.32,.04)*100) +
  coord_trans(y='sqrt')

summary(ld$EstimatedEffectiveYield)

# ... Associated estimated loss ...
ggplot(data = ld
       ,aes(x = EstimatedLoss)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins = 75) +
  scale_x_continuous(breaks = seq(.0045,.3661,.05), labels = seq(.0048,.3661,.05)*100) +
  scale_y_continuous(breaks = seq(0,15000,512)*2) +
  coord_trans(y='sqrt')

summary(ld$EstimatedLoss)

# ... Borrower rate distribution ...
ggplot(data = ld
       ,aes(x = BorrowerRate)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=100) +
  scale_x_continuous(breaks = seq(.0,.37,.1), labels = seq(.0,.37,.1)*100)

summary(ld$BorrowerRate)
```

```{r}
# OBSERVE THE ESTIMATED EFFECTIVE YIELD BY SUBSETING TO HIGHER RISK INVESTMENTS AND LOWER RISK
lower_risk <- ggplot(data = subset(ld, ProsperRating..Alpha. <= 'C'),
       aes(x = EstimatedEffectiveYield)) +
  ggtitle('Lower Risk Investments (AA - C)') +
  xlab("Estimated Effective Yield (%)") +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=20) +
  scale_x_continuous(breaks = seq(-.2,.32,.05), labels = seq(-.2,.32,.05)*100) +
  coord_trans(y='sqrt')

higher_risk <- ggplot(data = subset(ld, ProsperRating..Alpha. > 'C'),
       aes(x = EstimatedEffectiveYield)) +
  ggtitle('Higher Risk Investments (D - HR)') +
  xlab("Estimated Effective Yield (%)") +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=20) +
  scale_x_continuous(breaks = seq(-.2,.32,.05), labels = seq(-.2,.32,.05)*100) +
  coord_trans(y='sqrt')

grid.arrange(lower_risk, higher_risk, nrow=2)
```

```{r}
ggplot(data = ld,
       aes(x = ProsperScore)) +
  geom_histogram(color = I('black')
                 ,fill = I('#099DD9')
                 ,bins = 11) +
  scale_x_continuous(breaks = c(1:11))

summary(ld$ProsperScore)
```


```{r}
library(psych)
?describe(ld)
```
