---
output: 
  html_document: 
    smart: no
---
# Loan Data from Prosper
**_by Bruno de Assis Pereira_**

---

In this project, I am going to present an **Exploratory Data Analysis** over a dataset that contains informations about **Loans**. This dataset belongs to [Prosper](https://www.prosper.com/) and it contains **_113,937 loans_** with **_81 variables_** on each loan.

The **Loan Data from Prosper** presents a lot of informations about the profile of a borrower that can be found by analysing the *Listings*. By analysing this dataset, I intend to provide useful information that enables a investor to safely select the best option of loan to apply.

A data dictionary was provided to aid through the whole process, this can be found in the **appendix** by the end of this document.

Let's begin!

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Loading all of the packages that are going to be used during the analysis

library(ggplot2)
library(knitr)
library(dplyr)
library(GGally)
library(gridExtra)
library(skimr)
```

## Understanding the data
```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd('C:/Users/Bruno/Documents/Udacity/R/Project')

loanData <- read.csv('../prosperLoanData.csv')
str(loanData)
```

Since we have more than 80 variables, for this first moment, I want to select variables that can be related somehow and reduce the number of analysed variables.
To aid me over this selection process, I am making use of the *ggpairs* function.

```{r warning=FALSE, message=FALSE, fig.width=14, fig.height=14, correlation_matrix}
# Reordering factor variables
LoanStatus_ord_lvl <- c(levels(loanData$LoanStatus)[1:6]
      ,levels(loanData$LoanStatus)[8:12]
      ,'Past Due (>120 days)')
loanData$LoanStatus <- ordered(loanData$LoanStatus, levels = LoanStatus_ord_lvl)

ProsperRating_ord_lvl <- c('', 'AA', 'A', levels(loanData$ProsperRating..Alpha.)[4:8])
loanData$ProsperRating..Alpha. <- ordered(loanData$ProsperRating..Alpha., levels = ProsperRating_ord_lvl)

# Enabling reproducible results.
set.seed(2)

# Defining a list of columns to be analysed
columns_list <- c('LoanStatus'
                  ,'LoanOriginalAmount'
                  ,'BorrowerRate'
                  ,'EstimatedEffectiveYield'
                  ,'EstimatedLoss'
                  ,'ProsperRating..Alpha.'
                  ,'ProsperScore'
                  ,'CurrentDelinquencies'
                  ,'StatedMonthlyIncome'
                  ,'Recommendations'
                  ,'InvestmentFromFriendsCount')

# Sampling the original dataset so it can be used in a correlation matrix
loanData_samp <- loanData[sample(1:nrow(loanData), 10000), columns_list]

# Plotting the matrix
# ggpairs(loanData_samp
#         ,axisLabels = 'internal')
```

This plot brings a nice overview over the relationships among the selected variables. By providing scatterplots, histograms, box plots and correlation coeficients, this matrix starts to give some sense over the data behavior. For instance, if we take the variables _BorrowerRate_ and _EstimatedEffectiveYield_, we can see that they are positively correlated by looking to the _coeficient_ and to the _scatterplot_.

DESCRIBE MORE ABOUT THE CORRELATION MATRIX

With that in mind, let's take a closer look over each of these variables.

```{r warning=FALSE, message=FALSE, subsetting_data}
#
# ...Removing loan registries that originated before July 2009...
# ...This can be done by subsetting our dataset...
# ...The 'columns_list' defined earlier will be used from now on...
#

ld <- subset(loanData
       ,as.Date(LoanOriginationDate) >= as.Date('2009-07-01')
       ,select = columns_list
       )

str(ld)
```

## Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

Analysing how the Loan Status variable is distributed
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplot(data = ld
       ,aes(x = LoanStatus)) +
  geom_histogram(color = I('black')
                 ,fill = I('#099DD9')
                 ,stat='count') +
  theme_bw(base_size = 10) +
  theme(axis.text.x=element_text(angle=60,hjust=1))

table(ld$LoanStatus)
```

Analysing how the Loan Amount variable is distributed
```{r warning=FALSE, message=FALSE}
plot1 <- ggplot(data = ld
       ,aes(x = LoanOriginalAmount)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,binwidth = 1000) +
  scale_x_continuous(breaks = seq(0,35000,2500))

plot2 <- ggplot(data = ld
       ,aes(x = LoanOriginalAmount)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,binwidth = .05) +
  scale_x_log10()

grid.arrange(plot1, plot2, nrow=2)

summary(ld$LoanOriginalAmount)
```

Analysing how the Listings are distributed across the Risk Ratings
```{r warning=FALSE, message=FALSE}
ggplot(data = ld
       ,aes(x = ProsperRating..Alpha.)) +
  geom_histogram(color = I('black')
                 ,fill = I('#099DD9')
                 ,stat='count')

# ... Associated effective yield of investment in percent ...
ggplot(data = ld
       ,aes(x = EstimatedEffectiveYield)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=50) +
  scale_x_continuous(breaks = seq(-.2,.32,.04), labels = seq(-.2,.32,.04)*100) +
  coord_trans(y='sqrt')

summary(ld$EstimatedEffectiveYield)

# ... Associated estimated loss ...
ggplot(data = ld
       ,aes(x = EstimatedLoss)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins = 75) +
  scale_x_continuous(breaks = seq(.0045,.3661,.05), labels = seq(.0048,.3661,.05)*100) +
  scale_y_continuous(breaks = seq(0,15000,512)*2) +
  coord_trans(y='sqrt')

summary(ld$EstimatedLoss)

# ... Borrower rate distribution ...
ggplot(data = ld
       ,aes(x = BorrowerRate)) +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=100) +
  scale_x_continuous(breaks = seq(.0,.37,.1), labels = seq(.0,.37,.1)*100)

summary(ld$BorrowerRate)
```

```{r}
# OBSERVE THE ESTIMATED EFFECTIVE YIELD BY SUBSETING TO HIGHER RISK INVESTMENTS AND LOWER RISK
lower_risk <- ggplot(data = subset(ld, ProsperRating..Alpha. <= 'C'),
       aes(x = EstimatedEffectiveYield)) +
  ggtitle('Lower Risk Investments (AA - C)') +
  xlab("Estimated Effective Yield (%)") +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=20) +
  scale_x_continuous(breaks = seq(-.2,.32,.05), labels = seq(-.2,.32,.05)*100) +
  coord_trans(y='sqrt')

higher_risk <- ggplot(data = subset(ld, ProsperRating..Alpha. > 'C'),
       aes(x = EstimatedEffectiveYield)) +
  ggtitle('Higher Risk Investments (D - HR)') +
  xlab("Estimated Effective Yield (%)") +
  geom_histogram(color = I('black')
                 ,fill = I('#ffc04d')
                 ,bins=20) +
  scale_x_continuous(breaks = seq(-.2,.32,.05), labels = seq(-.2,.32,.05)*100) +
  coord_trans(y='sqrt')

grid.arrange(lower_risk, higher_risk, nrow=2)
```

```{r}
ggplot(data = ld,
       aes(x = ProsperScore)) +
  geom_histogram(color = I('black')
                 ,fill = I('#099DD9')
                 ,bins = 11) +
  scale_x_continuous(breaks = c(1:11))

summary(ld$ProsperScore)
```


```{r}
library(psych)
describe(ld)
```

> **Tip**: Make sure that you leave a blank line between the start / end of
each code block and the end / start of your Markdown text so that it is
formatted nicely in the knitted text. Note as well that text on consecutive
lines is treated as a single space. Make sure you have a blank line between
your paragraphs so that they too are formatted for easy readability.

## Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


## Bivariate Plots Section

UNDERSTAND HOW THE LOAN AMOUNT IS RELATED TO THE RISK

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}

```

## Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


## Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

## Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

## Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

## Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!

------

## Appendix

Variable | Description
------------- | -------------
ListingKey | Unique key for each listing, same value as the 'key' used in the listing object in the API.
ListingNumber | The number that uniquely identifies the listing to the public as displayed on the website.
ListingCreationDate | The date the listing was created.
CreditGrade | The Credit rating that was assigned at the time the listing went live. Applicable for listings pre-2009 period and will only be populated for those listings.
Term | The length of the loan expressed in months.
LoanStatus | The current status of the loan: Cancelled,  Chargedoff, Completed, Current, Defaulted, FinalPaymentInProgress, PastDue. The PastDue status will be accompanied by a delinquency bucket.
ClosedDate | Closed date is applicable for Cancelled, Completed, Chargedoff and Defaulted loan statuses. 
BorrowerAPR | The Borrower's Annual Percentage Rate (APR) for the loan.
BorrowerRate | The Borrower's interest rate for this loan. 
LenderYield | The Lender yield on the loan. Lender yield is equal to the interest rate on the loan less the servicing fee.
EstimatedEffectiveYield | Effective yield is equal to the borrower interest rate (i) minus the servicing fee rate, (ii) minus estimated uncollected interest on charge-offs, (iii) plus estimated collected late fees.  Applicable for loans originated after July 2009.
EstimatedLoss | Estimated loss is the estimated principal loss on charge-offs. Applicable for loans originated after July 2009.
EstimatedReturn | The estimated return assigned to the listing at the time it was created. Estimated return is the difference between the Estimated Effective Yield and the Estimated Loss Rate. Applicable for loans originated after July 2009.
ProsperRating (numeric) | The  Prosper Rating assigned at the time the listing was created: 0 - N/A, 1 - HR, 2 - E, 3 - D, 4 - C, 5 - B, 6 - A, 7 - AA.  Applicable for loans originated after July 2009.
ProsperRating (Alpha) | The Prosper Rating assigned at the time the listing was created between AA - HR.  Applicable for loans originated after July 2009.
ProsperScore | A custom risk score built using historical Prosper data. The score ranges from 1-10, with 10 being the best, or lowest risk score.  Applicable for loans originated after July 2009.
ListingCategory | The category of the listing that the borrower selected when posting their listing: 0 - Not Available, 1 - Debt Consolidation, 2 - Home Improvement, 3 - Business, 4 - Personal Loan, 5 - Student Use, 6 - Auto, 7- Other, 8 - Baby&Adoption, 9 - Boat, 10 - Cosmetic Procedure, 11 - Engagement Ring, 12 - Green Loans, 13 - Household Expenses, 14 - Large Purchases, 15 - Medical/Dental, 16 - Motorcycle, 17 - RV, 18 - Taxes, 19 - Vacation, 20 - Wedding Loans
BorrowerState | The two letter abbreviation of the state of the address of the borrower at the time the Listing was created.
Occupation | The Occupation selected by the Borrower at the time they created the listing.
EmploymentStatus | The employment status of the borrower at the time they posted the listing.
EmploymentStatusDuration | The length in months of the employment status at the time the listing was created.
IsBorrowerHomeowner | A Borrower will be classified as a homowner if they have a mortgage on their credit profile or provide documentation confirming they are a homeowner.
CurrentlyInGroup | Specifies whether or not the Borrower was in a group at the time the listing was created.
GroupKey | The Key of the group in which the Borrower is a member of. Value will be null if the borrower does not have a group affiliation.
DateCreditPulled | The date the credit profile was pulled. 
CreditScoreRangeLower | The lower value representing the range of the borrower's credit score as provided by a consumer credit rating agency.
CreditScoreRangeUpper | The upper value representing the range of the borrower's credit score as provided by a consumer credit rating agency. 
FirstRecordedCreditLine | The date the first credit line was opened.
CurrentCreditLines | Number of current credit lines at the time the credit profile was pulled.
OpenCreditLines | Number of open credit lines at the time the credit profile was pulled.
TotalCreditLinespast7years | Number of credit lines in the past seven years at the time the credit profile was pulled.
OpenRevolvingAccounts | Number of open revolving accounts at the time the credit profile was pulled.
OpenRevolvingMonthlyPayment | Monthly payment on revolving accounts at the time the credit profile was pulled.
InquiriesLast6Months | Number of inquiries in the past six months at the time the credit profile was pulled.
TotalInquiries | Total number of inquiries at the time the credit profile was pulled.
CurrentDelinquencies | Number of accounts delinquent at the time the credit profile was pulled.
AmountDelinquent | Dollars delinquent at the time the credit profile was pulled.
DelinquenciesLast7Years | Number of delinquencies in the past 7 years at the time the credit profile was pulled.
PublicRecordsLast10Years | Number of public records in the past 10 years at the time the credit profile was pulled.
PublicRecordsLast12Months | Number of public records in the past 12 months at the time the credit profile was pulled.
RevolvingCreditBalance | Dollars of revolving credit at the time the credit profile was pulled.
BankcardUtilization | The percentage of available revolving credit that is utilized at the time the credit profile was pulled.
AvailableBankcardCredit | The total available credit via bank card at the time the credit profile was pulled.
TotalTrades | Number of trade lines ever opened at the time the credit profile was pulled.
TradesNeverDelinquent | Number of trades that have never been delinquent at the time the credit profile was pulled.
TradesOpenedLast6Months | Number of trades opened in the last 6 months at the time the credit profile was pulled.
DebtToIncomeRatio | The debt to income ratio of the borrower at the time the credit profile was pulled. This value is Null if the debt to income ratio is not available. This value is capped at 10.01 (any debt to income ratio larger than 1000% will be returned as 1001%).
IncomeRange | The income range of the borrower at the time the listing was created.
IncomeVerifiable | The borrower indicated they have the required documentation to support their income.
StatedMonthlyIncome | The monthly income the borrower stated at the time the listing was created.
LoanKey | Unique key for each loan. This is the same key that is used in the API. 
TotalProsperLoans | Number of Prosper loans the borrower at the time they created this listing. This value will be null if the borrower had no prior loans. 
TotalProsperPaymentsBilled | Number of on time payments the borrower made on Prosper loans at the time they created this listing. This value will be null if the borrower had no prior loans.
OnTimeProsperPayments | Number of on time payments the borrower had made on Prosper loans at the time they created this listing. This value will be null if the borrower has no prior loans.
ProsperPaymentsLessThanOneMonthLate | Number of payments the borrower made on Prosper loans that were less than one month late at the time they created this listing. This value will be null if the borrower had no prior loans. 
ProsperPaymentsOneMonthPlusLate | Number of payments the borrower made on Prosper loans that were greater than one month late at the time they created this listing. This value will be null if the borrower had no prior loans.
ProsperPrincipalBorrowed | Total principal borrowed on Prosper loans at the time the listing was created. This value will be null if the borrower had no prior loans.
ProsperPrincipalOutstanding | Principal outstanding on Prosper loans at the time the listing was created. This value will be null if the borrower had no prior loans.
ScorexChangeAtTimeOfListing | Borrower's credit score change at the time the credit profile was pulled. This will be the change relative to the borrower's last Prosper loan. This value will be null if the borrower had no prior loans.
LoanCurrentDaysDelinquent | The number of days delinquent. 
LoanFirstDefaultedCycleNumber | The cycle the loan was charged off. If the loan has not charged off the value will be null. 
LoanMonthsSinceOrigination | Number of months since the loan originated.
LoanNumber | Unique numeric value associated with the loan.
LoanOriginalAmount | The origination amount of the loan.
LoanOriginationDate | The date the loan was originated.
LoanOriginationQuarter | The quarter in which the loan was originated.
MemberKey | The unique key that is associated with the borrower. This is the same identifier that is used in the API member object. 
MonthlyLoanPayment | The scheduled monthly loan payment.
LP_CustomerPayments | Pre charge-off cumulative gross payments made by the borrower on the loan. If the loan has charged off, this value will exclude any recoveries.
LP_CustomerPrincipalPayments | Pre charge-off cumulative principal payments made by the borrower on the loan. If the loan has charged off, this value will exclude any recoveries.
LP_InterestandFees | Pre charge-off cumulative interest and fees paid by the borrower. If the loan has charged off, this value will exclude any recoveries.
LP_ServiceFees | Cumulative service fees paid by the investors who have invested in the loan. 
LP_CollectionFees | Cumulative collection fees paid by the investors who have invested in the loan.
LP_GrossPrincipalLoss | The gross charged off amount of the loan.
LP_NetPrincipalLoss | The principal that remains uncollected after any recoveries.
LP_NonPrincipalRecoverypayments | The interest and fee component of any recovery payments. The current payment policy applies payments in the following order: Fees, interest, principal.
PercentFunded | Percent the listing was funded.
Recommendations | Number of recommendations the borrower had at the time the listing was created.
InvestmentFromFriendsCount | Number of friends that made an investment in the loan.
InvestmentFromFriendsAmount | Dollar amount of investments that were made by friends.
Investors | The number of investors that funded the loan.